Automatic Disease Diagnosis Using Large Language Models and Answer Set Programming

### 2025-06-08 paper/draft.tex
Fix caption
Signed-off-by: Evangelos Lamprou <vagos@lamprou.xyz>
Set name
Signed-off-by: Evangelos Lamprou <vagos@lamprou.xyz>
Improve caption
Signed-off-by: Evangelos Lamprou <vagos@lamprou.xyz>

\newcommand{\sys}{\textsc{Sys}\xspace}

@@

\end{tikzpicture}
\end{center}
\caption{The diagnostic process begins by transforming medical literature 
    into an ASP program using a LLM. 
    An ASP solver then executes the program and produces a final diagnosis 
    based on each patient’s data.}
    \label{fig:architecture}
\end{figure}

@@

\caption{A simple prompt that does not yield satisfactory results.}
\label{fig:bad-prompt}
\end{figure}

@@

diagnosis(pneumonia) :- has(symptom(cough_with_mucus)),
                        has(symptom(chest_pain)),
...
\end{verbatim}
\end{commandline}
\caption{An effective prompt that produces accurate and well-structured output.}
\label{fig:good-prompt}
\end{figure}

>>>>

\newcommand{\sys}{\textsc{McCoy}\xspace}

@@

\end{tikzpicture}
\end{center}
	\caption{\textbf{\sys overview.} The diagnostic process begins by transforming medical literature 
    into an ASP program using a LLM. 
    An ASP solver then executes the program and produces a final diagnosis 
    based on each patient’s data.}
    \label{fig:architecture}
\end{figure}

@@

\caption{A prompt that does not yield satisfactory results. The LLM output does not decompose the disease diagnosis into discrete rules.}
\label{fig:bad-prompt}
\end{figure}

@@

diagnosis(pneumonia) :- has(symptom(cough_with_mucus)),
                        has(symptom(chest_pain)),
...
\end{verbatim}
\end{commandline}
\caption{An effective prompt that produces accurate and well-structured output.
	The LLM output is structured into multiple rules that aid explainability and can result in partial diagnoses.}
\label{fig:good-prompt}
\end{figure}
